---
title: "GPA Project"
author: "Nick Tandle"
date: "2/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Packages:
```{r}
install.packages("rvest")
install.packages("stringr")
install.packages("readxl")

library("rvest")
library("stringr")
library("readxl")
```


Getting Course GPA Dataset
```{r, eval=FALSE}
wade_datasetV2 <- read_excel("Wade_DatasetV2.xlsx",
                             sheet = "TestSpring2018")
```


Creation of URLs for extraction
```{r}
course_abbreviations= unique(wade_datasetV2$Subject)

final_course_urls= paste0("http://catalog.illinois.edu/courses-of-instruction/",tolower(course_abbreviations),"/")
```


Extracting credit hours from the URLs  of each course.

Not generalized yet:
```{r}
Course_credits =
  read_html(psyc) %>%
  html_nodes(".courseblocktitle") %>%
  html_text() %>%
  str_extract_all(, pattern = "credit:[:blank:][:digit:][:blank:]to[:blank:][:digit:]|credit:[:blank:][:digit:]")
```


Extracting course abbreviation to combine with credit hour

Not generalized yet:
```{r}
Course_abbreviations=
read_html(psyc) %>%
  html_nodes(".courseblocktitle") %>%
  html_text() %>%
  str_extract_all(pattern= "PSYC[:blank:][:digit:]{3}") %>%
  str_replace_all(pattern = "[:blank:]", replacement = "")
```


Function that merges course abbreviations and credit hours
```{r}


```

^^^^^^^^^^^^^^^^Check notebook for ideas.

check the fizzbuzz homework assignment for generalizing function to allow for multiple x values
