---
title: "GPAProjectProjectionScraps"
author: "Nick Tandle"
date: "2/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

**Testing merging abrev and credit hours
```{r}
test_credit = as.character(testing_credits)
test_abrev = as.character(Psych_course_abbreviations)
psyc_final = data.frame(as.vector(test_abrev), as.vector(test_credit))

```



Now creating a generalized program that will extract the course names and their corresponding credit hours from the list of all college department URLs.

Showing first few urls to be put into function.
```{r}
head(final_course_urls)

```

Small subset of URLS for testing as I create function:
```{r}
Some_Course_URLs=head(final_course_urls)

```


```{r}
test_url="http://catalog.illinois.edu/courses-of-instruction/ae/"

abb_function(test_url)


{
read_html(test_url) %>%
  html_nodes(".schedlink") %>%
  html_text() %>%
  str_extract_all(pattern= "[:alpha:]{3,4}[:blank:][:digit:]{3}") %>%
  str_replace_all(pattern = "[:blank:]", replacement = "")
}


test= mapply(FUN = abb_function, Some_Course_URLs)
test2= mapply(FUN = credit_function, Some_Course_URLs)
test2

engl_url="http://catalog.illinois.edu/courses-of-instruction/engl/"
abb_function(engl_url)
credit_function(engl_url)


  read_html(engl_url) %>%
  html_nodes(".courseblocktitle") %>%
  html_text() %>%
  str_extract_all(, pattern = "credit:[:blank:][:digit:]")
```


```{r}
  read_html(engl_url) %>%
  html_nodes(".courseblocktitle") %>%
  html_text() %>%
  str_extract_all(, pattern = "credit:[:blank:][:digit:][:blank:]to[:blank:][:digit:]|credit:[:blank:][:digit:]")
```



figuring out combining the credits and abbreviations:
```{r}
head_abb=head(all_abbreviations,2)
head_credit= head(all_credits,2)

combined_head_abb= c(all_abbreviations)
combined_head_abb

all_head= data.frame(as.vector(head_abb), as.vector(head_credit))


do.call(rbind, Map(data.frame, A=as.character(head_abb), B=as.character(head_credit)))

summary(head_abb)
summary(as.character(head_credit))
```



```{r}
install.packages("dplyr")
library(dplyr)

head_abb_test= data.frame(unlist(head_abb, head_credit))
head_credit_test= data.frame(unlist(head_credit))

head_test_all= bind_cols(head_abb_test,head_credit_test)

colnames(head_test_all)=c("abb", "credit")
head_test_all
```


```{r}
rm(head_abb_test)
rm(head_credit_test)
rm(head_test_all)

rm(df3)
```



continued effrots to merge un even full lists of abbreveations and credits:
```{r}
df_abb= data.frame(unlist(all_abbreviations))
df_credit= data.frame(unlist(all_credits))

colnames(head_test_all)=c("abb", "credit")
head_test_all

test_abb= head(df_abb)
```

```{r}
test_abb_names= setNames(cbind(rownames(test_abb), test_abb, row.names= NULL),
                         c("url","abbreviation"))
test_abb_names
```

```{r}
rm(test_abb_names)
rm(test_abb)
rm(head_abb)
rm(head_credit)
```



continued cleaning of credit from semi final data frame:
```{r}
class(total_course_info$credit)

test_head_credit= head(total_course_info$credit)

str_replace(test_head_credit, pattern = "credit:[:blank:]", replacement = "")

str_view(test_head_credit, pattern = "credit")

```

```{r}
rm(engl_url)
rm(test_head_credit)
rm(head_abb)
rm(head_credit)
rm(combined_head_abb)
rm(result.df)
rm(result)
rm(test)
```




































